Kids PM Summary

### 2019-12-04 data_cleaning_initial.Rmd
additional dusttrack data cleaning

---
title: "KidsAIR initial data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019"
output: pdf_document
---

@@

# Load, format, and save KidsAIR Dusttrack data
```{r}
# Load Dusttrack data
## List sheets within the excel file
list_sheets_nm <- excel_sheets("Input/nm_kids_dusttrack_20191121.xlsx")
## Apply the read_xlsx function to each item in the sheet list
## Bind the items from each sheet into a single dataframe
pm_initial_nm <- data.frame(do.call("rbind", lapply(list_sheets_nm, read_xlsx, 
                                      path = "Input/nm_kids_dusttrack_20191121.xlsx"))) %>% 
  mutate(area = "NM")

@@

# Load, format, and save home and child overview data
## These files will link the home ID and child ID with the intervention status
```{r}
# Load files
wmt_child_initial <- read_xlsx("Input/wmt_child_20191126.xlsx")
wmt_home_initial <- read_xlsx("Input/wmt_home_20191126.xlsx")
wmt_homewinter_initial <- read_xlsx("Input/wmt_homewinter_20191126.xlsx")
wmt_parent_demographics_initial <- read_xlsx("Input/wmt_parent_demographics_20191126.xlsx")

@@

>>>>

---
title: "KidsAIR initial data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 4 Dec 2019"
output: pdf_document
---

@@

# Load, format, and save KidsAIR Dusttrack data
```{r}
##### Read in dusttrack .txt files (from WMT location) #####

# List files
list_txt_files <- list.files("Input/WMT/dusttrack_txt_files")

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd("Input/WMT/dusttrack_txt_files")
initial_data = tibble(file_list = list_txt_files) %>%
  extract(file_list, "home_winter_id", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 28)) %>%
  unnest(save_data) %>%
  select(-file_list)

# Format combined file from above; combine with other WMT/PM data below
wmt_pm_txt <- initial_data %>% 
  mutate(date = mdy(`MM/dd/yyyy`),
         time = hms(`hh:mm:ss`),
         pm = as.numeric(`mg/m^3`),
         area = "WMT") %>% 
  select(home_winter_id, date, time, pm, area)

##### Next, load other files from all locations #####

##### Load combined dusttrack files from Emily W #####
##### Compare these with the raw data pulled in above #####

## List sheets within the excel file
list_sheets_nn <- excel_sheets("Input/nn_kids_dusttrack_20191121.xlsx")
## Apply the read_xlsx function to each item in the sheet list
## Bind the items from each sheet into a single dataframe
pm_initial_nn <- data.frame(do.call("rbind", lapply(list_sheets_nn, read_xlsx, 
                                      path = "Input/nn_kids_dusttrack_20191121.xlsx"))) %>% 
  mutate(area = "NN")

@@

# Load, format, and save home and child overview/demographic data
```{r}
# Load files
wmt_child_initial <- read_xlsx("Input/wmt_child_20191126.xlsx")
wmt_home_initial <- read_xlsx("Input/wmt_home_20191126.xlsx")
wmt_homewinter_initial <- read_xlsx("Input/wmt_homewinter_20191126.xlsx")
wmt_parent_demographics_initial <- read_xlsx("Input/wmt_parent_demographics_20191126.xlsx")

@@

```{r}

```

### 2019-12-04 pm_summary.Rmd
additional dusttrack data cleaning

# Summary stats
```{r}
summary_kids_pm <- kids_pm %>% 
  summarize(mean(pm_24hr_mean), sd(pm_24hr_mean),
            min(pm_24hr_mean), max(pm_24hr_mean),
            min(pm), max(pm),
            min(pm_sampling_days), max(pm_sampling_days),
            min(pm_total_observations), max(pm_total_observations)) %>% 
  t()
summary_kids_pm
```

>>>>

# Summary stats
```{r}
summary_kids_pm <- kids_pm %>% 
  #filter(pm < 0)
  summarize(mean(pm_24hr_mean), sd(pm_24hr_mean),
            min(pm_24hr_mean), max(pm_24hr_mean),
            min(pm), max(pm), mean(pm_total_days),
            min(pm_total_days), max(pm_total_days),
            min(pm_total_observations), max(pm_total_observations),
            mean(pm_24hr_daily), mean(pm_24hr_daily_weighted)) %>% 
  t()
summary_kids_pm
```
